Deep Learning

### 2015-01-11 deepreview.tex
Update deepreview.tex
added a sentence and 2 references on the advantage of deep representations over classical non-parametric methods

\section{Introduction}

@@

The issue of representation lies at the heart of the debate between the
logic-inspired and the neurally-inspired paradigms for cognition. In the
logic-inspired paradigm, an instance of a symbol is something whose only
property is that it is either identical or non-identical to other symbol
instances. It has no internal structure that is relevant to its use. By
contrast, neural networks use large activity vectors instead of symbols and
parallel matrix operations followed by non-linearities instead of formal
rules of inference. The elements of such vectors can be understood as
the values of learned attributes (or features) associated with some object. 
With sufficient data, computational power and depth,
the combination of backpropagation for computing gradients and stochastic
gradient descent for updating the weights on connections has proved to be
very good at learning appropriate distributed representations. These
representations allow a lot of parallel computation at the feature level so
that complex tasks can be solved in a very small number of sequential
steps. In fact, it can be shown that a measure of the richness of the functions
that can be represented by a deep neural network grows exponentially
with depth~\citep{Montufar-et-al-NIPS2014}.

>>>>

%% this comment is geoff practising using github %%%
\section{Introduction}

@@

The issue of representation lies at the heart of the debate between the
logic-inspired and the neurally-inspired paradigms for cognition. In the
logic-inspired paradigm, an instance of a symbol is something whose only
property is that it is either identical or non-identical to other symbol
instances. It has no internal structure that is relevant to its use. By
contrast, neural networks use large activity vectors instead of symbols and
parallel matrix operations followed by non-linearities instead of formal
rules of inference. The elements of such vectors can be understood as
the values of learned attributes (or features) associated with some object. 
With sufficient data, computational power and depth,
the combination of backpropagation for computing gradients and stochastic
gradient descent for updating the weights on connections has proved to be
very good at learning appropriate distributed representations. These
representations allow a lot of parallel computation at the feature level so
that complex tasks can be solved in a very small number of sequential
steps. In fact, it can be shown that a measure of the richness of the functions
that can be represented by a deep neural network grows exponentially
with depth~\citep{Montufar-et-al-NIPS2014}, whereas according to the
same measure, classical (shallow) non-parametric statistical methods such as
Gaussian Support Vector Machines~\citep{Bengio-localfailure-NIPS-2006-small} 
or decision trees~\citep{Bengio-decision-trees10}
would require an exponentially large number
of training examples to represent the same kinds of functions.
